### 2020-10-28 soyherb.Rmd
nnn

---
title: "Soybean herbicide study - Dan Smith"
author: "Maxwel Coura Oliveira"
date: "10/28/2020"
output: 
  html_document: 
    toc: yes
    highlight: zenburn
    theme: simplex
    number_sections: yes
---

# Load packages

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(emmeans)
library(glmmTMB)
library(kableExtra)
```

# Load dataset

```{r echo=TRUE, message=FALSE, warning=FALSE}
data <- read_csv("SB12.csv")
```

## Glimpse dataset

```{r echo=TRUE, message=FALSE, warning=FALSE}
glimpse(data)
```

## Skim dataset

```{r echo=TRUE, message=FALSE, warning=FALSE}
skimr::skim(data)
```

# Data visualization

## Waterhemp control at 14 DAT

```{r fig.align='center'}
ggplot(data, aes(x=reorder(other,waterhempcontrol_14), y=waterhempcontrol_14,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Waterhemp control at 28 DAT

```{r fig.align='center'}
ggplot(data, aes(x=reorder(other,waterhempcontrol_28), y=waterhempcontrol_28,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Waterhemp control at harvest

```{r fig.align='center', message=FALSE, warning=FALSE}
ggplot(data, aes(x=reorder(other,waterhempcontrol_harvest), y=waterhempcontrol_harvest,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Yield (bu/acre)

```{r message=FALSE, warning=FALSE, fig.align='center'}
ggplot(data, aes(x=reorder(other,yield_bu), y=yield_bu,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```
# Data wrangling

```{r}
new_dt <- 
  data %>% 
  rename (herbicide = other) %>% 
  mutate(
    wt_14 = waterhempcontrol_14/100,
    wt_28 = waterhempcontrol_28/100,
    yield_kg = yield_bu * 67.5) %>% 
  mutate(
    wt_14 = 
      case_when(
        waterhempcontrol_14 == 100   ~  0.99,
        TRUE            ~ wt_14),
    wt_28 = case_when(
        waterhempcontrol_28 == 100   ~  0.99,
        waterhempcontrol_28 == 0   ~  0.01,
        TRUE            ~ wt_28)) %>% 
  filter(
    herbicide != "PRE only"
  )
```

# Data analysis

## Waterhemp control at 14 DAT

### Model

* Model using herbicide trts, year, and location as fixed effects. Only rep as random effects

```{r message=FALSE, warning=FALSE}
model_14 <- glmmTMB(wt_14 ~ herbicide * location * year + (1|rep), beta_family(link = "logit"), data=new_dt)
```

### Anova

```{r message=FALSE, warning=FALSE}
glmmTMB:::Anova.glmmTMB(model_14)
```

* Anova shows no interaction of year, herbicide and location. There is only herbicide and year effects

### New model

Model using herbicide trt as fixed, and rep, year, and location as random effects

```{r message=FALSE, warning=FALSE}
model_14_2 <- glmmTMB(wt_14 ~ herbicide + (1|rep) + (1|location/year), beta_family(link = "logit"), data=new_dt)
```

### New Anova

```{r message=FALSE, warning=FALSE}
glmmTMB:::Anova.glmmTMB(model_14_2)
```

- No effects of herbicide treatments. However, I am looking into herbicide effects.

### Least square means

```{r }
lsmeans_14<- emmeans(model_14_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
```

### Compact letter display

```{r fig.align='center'}
plot(lsmeans_14, ~ herbicide, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
```

```{r message=FALSE, warning =FALSE}
CLD(lsmeans_14$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

## Waterhemp control at 28 DAT

### Model

* Model using herbicide trts, year, and location as fixed effects. Only rep as random effects

```{r message=FALSE, warning=FALSE}
model_28 <- glmmTMB(wt_28 ~ herbicide * location * year + (1|rep), beta_family(link = "logit"), data=new_dt)
```

### Anova

```{r message=FALSE, warning=FALSE}
glmmTMB:::Anova.glmmTMB(model_28)
```

* Anova shows no interaction of year, herbicide and location. There is only herbicide and year effects

### New model

Model using herbicide trt as fixed, and rep, year, and location as random effects

```{r message=FALSE, warning=FALSE}
model_28_2 <- glmmTMB(wt_28 ~ herbicide + (1|rep) + (1|location/year), beta_family(link = "logit"), data=new_dt)
```

### New Anova

```{r message=FALSE, warning=FALSE}
glmmTMB:::Anova.glmmTMB(model_28_2)
```

- No effects of herbicide treatments

### Least square means

#### Herbicide

```{r }
lsmeans_28<- emmeans(model_28_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
```

### Plot

```{r fig.align='center'}
plot(lsmeans_28, ~ herbicide, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
```

### Compact letter display

```{r message=FALSE, warning =FALSE}
CLD(lsmeans_28$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

```{r include=FALSE}
if(requireNamespace("multcomp")) {
    multcomp::cld(lsmeans_28$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
}
```

### 2020-10-28 analysis/analysis.Rmd
as

---
title: "Soybean Glufosinate Study"
date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    highlight: kate
---

```{r setup, echo=FALSE, cache=FALSE}
library(knitr)
library(rmdformats)

## Global options
options(max.print="75")
opts_chunk$set(echo=FALSE,
	             cache=TRUE,
               prompt=FALSE,
               tidy=TRUE,
               comment=NA,
               message=FALSE,
               warning=FALSE)
opts_knit$set(width=75)
```

# Load packages

```{r echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(emmeans)
library(glmmTMB)
library(kableExtra)
library(lme4)
library(lmerTest)
```

# Load dataset

```{r echo=TRUE, message=FALSE, warning=FALSE}
data <- read_csv("SB12.csv")
```

## Glimpse dataset

```{r echo=TRUE, message=FALSE, warning=FALSE}
glimpse(data)
```

## Skim dataset

```{r echo=TRUE, message=FALSE, warning=FALSE}
skimr::skim(data)
```

# Data visualization

## Waterhemp control at 14 DAT

```{r fig.align='center', message=FALSE, warning=FALSE, echo=TRUE}
ggplot(data, aes(x=reorder(other,waterhempcontrol_14), y=waterhempcontrol_14,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Waterhemp control at 28 DAT

```{r fig.align='center', message=FALSE, warning=FALSE, echo=TRUE}
ggplot(data, aes(x=reorder(other,waterhempcontrol_28), y=waterhempcontrol_28,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Waterhemp control at harvest

```{r fig.align='center', message=FALSE, warning=FALSE, echo=TRUE}
ggplot(data, aes(x=reorder(other,waterhempcontrol_harvest), y=waterhempcontrol_harvest,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Weed biomass

```{r fig.align='center', message=FALSE, warning=FALSE, echo=TRUE}
ggplot(data, aes(x=reorder(other,biomass_gm2), y=biomass_gm2,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Weed biomass (g m2)") +
  theme_minimal() +
  theme(legend.position = "none")
```

## Yield (bu/acre)

```{r message=FALSE, warning=FALSE, fig.align='center', echo=TRUE}
ggplot(data, aes(x=reorder(other,yield_bu), y=yield_bu,
       fill=trade, color=trade)) +
  geom_boxplot(color="black") +
  geom_jitter(alpha=0.2) +
  facet_grid(year ~ location) +
  coord_flip() +
  labs(x="", y="Waterhemp control (%)") +
  theme_minimal() +
  theme(legend.position = "none")
```

# Data wrangling

```{r message=FALSE, warning=FALSE, echo=TRUE}
new_dt <- 
  data %>% 
  rename (herbicide = other) %>% 
  mutate(
    wt_14 = waterhempcontrol_14/100,
    wt_28 = waterhempcontrol_28/100,
    yield_kg = yield_bu * 67.5) %>% 
  mutate(
    wt_14 = 
      case_when(
        waterhempcontrol_14 == 100   ~  0.99,
        TRUE            ~ wt_14),
    wt_28 = case_when(
        waterhempcontrol_28 == 100   ~  0.99,
        waterhempcontrol_28 == 0   ~  0.01,
        TRUE            ~ wt_28)) %>% 
  filter(
    herbicide != "PRE only"
  )
```

# Data analysis

## Waterhemp control at 14 DAT

### Model

* Model using herbicide trts, year, and location as fixed effects. Only rep as random effects

```{r message=FALSE, warning=FALSE, echo=TRUE}
model_14 <- glmmTMB(wt_14 ~ herbicide * location * year + (1|rep), beta_family(link = "logit"), data=new_dt)
```

### Anova

```{r message=FALSE, warning=FALSE, echo=TRUE}
glmmTMB:::Anova.glmmTMB(model_14)
```

* Anova shows no interaction of year, herbicide and location. There is only herbicide and year effects

### New model

Model using herbicide trt as fixed, and rep, year, and location as random effects

```{r message=FALSE, warning=FALSE, echo=TRUE}
model_14_2 <- glmmTMB(wt_14 ~ herbicide + (1|rep) + (1|location/year), beta_family(link = "logit"), data=new_dt)
```

### New Anova

```{r message=FALSE, warning=FALSE, echo=TRUE}
glmmTMB:::Anova.glmmTMB(model_14_2)
```

- No effects of herbicide treatments. However, I am looking into herbicide effects.

### Least square means

```{r message=FALSE, warning=FALSE, echo=TRUE}
lsmeans_14<- emmeans(model_14_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
```

### Compact letter display

```{r fig.align='center', message=FALSE, warning=FALSE, echo=TRUE}
plot(lsmeans_14, ~ herbicide, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
```

```{r message=FALSE, warning=FALSE, echo=TRUE}
CLD(lsmeans_14$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

## Waterhemp control at 28 DAT

### Model

* Model using herbicide trts, year, and location as fixed effects. Only rep as random effects

```{r message=FALSE, warning=FALSE, echo=TRUE}
model_28 <- glmmTMB(wt_28 ~ herbicide * location * year + (1|rep), beta_family(link = "logit"), data=new_dt)
```

### Anova

```{r message=FALSE, warning=FALSE, echo=TRUE}
glmmTMB:::Anova.glmmTMB(model_28)
```

* Anova shows no interaction of year, herbicide and location. There is only herbicide and year effects

### New model

Model using herbicide trt as fixed, and rep, year, and location as random effects

```{r message=FALSE, warning=FALSE, echo=TRUE}
model_28_2 <- glmmTMB(wt_28 ~ herbicide + (1|rep) + (1|location/year), beta_family(link = "logit"), data=new_dt)
```

### New Anova

```{r message=FALSE, warning=FALSE, echo=TRUE}
glmmTMB:::Anova.glmmTMB(model_28_2)
```

- No effects of herbicide treatments

### Least square means

```{r message=FALSE, warning=FALSE, echo=TRUE}
lsmeans_28 <- emmeans(model_28_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
```

### Plot

```{r fig.align='center', echo=TRUE}
plot(lsmeans_28, ~ herbicide, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
```

### Compact letter display

```{r message=FALSE, warning =FALSE, echo=TRUE}
CLD(lsmeans_28$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

```{r include=FALSE}
if(requireNamespace("multcomp")) {
    multcomp::cld(lsmeans_28$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE)
}
```

## Yield

### Yield raw data distribution

```{r warning=FALSE, message=FALSE, echo=TRUE}
library(ggridges)
new_dt %>% 
  ggplot(
    aes(y=herbicide, x=yield_kg, fill=herbicide)) +
      geom_density_ridges(scale=2, show.legend = FALSE)
```

### Data manipulation

```{r warning=FALSE, message=FALSE, echo=TRUE}
yield_dt <- new_dt %>% 
  mutate(
    siteyr = case_when(
      location == "Lancaster" & year == 2020 ~ "Lan20",
      location == "Lancaster" & year == 2019 ~ "Lan19",
      location == "Brooklyn" & year == 2020 ~ "Bro20",
      location == "Brooklyn" & year == 2019 ~ "Bro19",
      TRUE                     ~  "siteyr"
    )
  )
```

### Model

```{r warning=FALSE, message=FALSE, echo=TRUE}
fit <- lmer(yield_kg ~ herbicide * siteyr + (1|rep), data=yield_dt)
```

### Anova

```{r echo=TRUE}
anova(fit)
```

### Least square means

```{r echo=TRUE}
lsmeans_fit <- emmeans(fit, ~ siteyr, cont="pairwise", adjust="none", alpha=0.05)
```

### Plot

```{r fig.align='center', echo=TRUE}
plot(lsmeans_fit, ~ siteyr, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
```

### Compact letter display

```{r message=FALSE, warning =FALSE, echo=TRUE}
CLD(lsmeans_fit$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
  kbl() %>%
  kable_classic_2(full_width = F)
```

<br><br>

```{r echo=FALSE, out.width=400, fig.align='center'}
knitr::include_graphics("https://media.giphy.com/media/l0Iyl55kTeh71nTXy/giphy.gif")
```

### 2020-10-28 soyherb.Rmd
as

@@
     toc: yes
-    highlight: zenburn
-    theme: simplex
+    theme: yeti
     number_sections: yes
+    toc_depth: 4
+    highlight: espresso
 ---
@@
 library(kableExtra)
+library(lme4)
+library(lmerTest)
 ```
@@
   labs(x="", y="Waterhemp control (%)") +
+  theme_minimal() +
+  theme(legend.position = "none")
+```
+
+## Weed biomass
+
+```{r fig.align='center', message=FALSE, warning=FALSE}
+ggplot(data, aes(x=reorder(other,biomass_gm2), y=biomass_gm2,
+       fill=trade, color=trade)) +
+  geom_boxplot(color="black") +
+  geom_jitter(alpha=0.2) +
+  facet_grid(year ~ location) +
+  coord_flip() +
+  labs(x="", y="Weed biomass (g m2)") +
   theme_minimal() +
@@
 
-#### Herbicide
-
 ```{r }
-lsmeans_28<- emmeans(model_28_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
+lsmeans_28 <- emmeans(model_28_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
 ```
@@
 ```
+
+## Yield
+
+### Yield raw data distribution
+
+```{r warning=FALSE, message=FALSE}
+library(ggridges)
+new_dt %>% 
+  ggplot(
+    aes(y=herbicide, x=yield_kg, fill=herbicide)) +
+      geom_density_ridges(scale=2, show.legend = FALSE)
+```
+
+### Data manipulation
+
+```{r warning=FALSE, message=FALSE}
+yield_dt <- new_dt %>% 
+  mutate(
+    siteyr = case_when(
+      location == "Lancaster" & year == 2020 ~ "Lan20",
+      location == "Lancaster" & year == 2019 ~ "Lan19",
+      location == "Brooklyn" & year == 2020 ~ "Bro20",
+      location == "Brooklyn" & year == 2019 ~ "Bro19",
+      TRUE                     ~  "siteyr"
+    )
+  )
+```
+
+### Model
+
+```{r warning=FALSE}
+fit <- lmer(yield_kg ~ herbicide * siteyr + (1|rep), data=yield_dt)
+```
+
+### Anova
+
+```{r}
+anova(fit)
+```
+
+### Least square means
+
+```{r }
+lsmeans_fit <- emmeans(fit, ~ siteyr, cont="pairwise", adjust="none", alpha=0.05)
+```
+
+### Plot
+
+```{r fig.align='center'}
+plot(lsmeans_fit, ~ siteyr, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
+```
+
+### Compact letter display
+
+```{r message=FALSE, warning =FALSE}
+CLD(lsmeans_fit$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
+  kbl() %>%
+  kable_classic_2(full_width = F)
+```
+
+<br><br>
+
+```{r echo=FALSE, out.width=400, fig.align='center'}
+knitr::include_graphics("https://media.giphy.com/media/l0Iyl55kTeh71nTXy/giphy.gif")
+```

### 2020-11-11 soyherb.Rmd
a

@@
 ```{r }
-lsmeans_14<- emmeans(model_14_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
+lsmeans_14 <- emmeans(model_14_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
 ```
@@
 
+```{r}
+nd14 <- data.frame(lsmeans_14$emmeans) %>% 
+  mutate(dat = "14 DAT")
+nd28 <- data.frame(lsmeans_28$emmeans)  %>% 
+  mutate(dat = "28 DAT")
+nd <- bind_rows(nd14, nd28)
+
+nd %>% 
+  mutate(herbicide = fct_relevel(herbicide, c("PRE fb glufosinate",
+                    "PRE fb glufosinate + acetochlor",
+                    "PRE fb glufosinate + dimethenamid-P",
+                    "PRE fb glufosinate + S-metolachlor",
+                    "PRE fb glufosinate + imazethapyr",
+                    "PRE fb glufosinate + fomesafen",
+                    "PRE fb glufosinate + pyroxasulfone",
+                    "PRE fb glufosinate + fomesafen + acetochlor",
+                    "PRE fb glufosinate + fomesafen + S-metolachlor"))) %>%
+ggplot(aes(x=herbicide, response, y=response*100)) + 
+  facet_wrap(~dat) +
+  coord_flip() + 
+  geom_point(size=3, color="#282728") + 
+  theme_bw() +  
+  labs(y="Waterhemp control (%)", x="", title="") +
+  geom_errorbar(aes(ymin  =  lower.CL*100, ymax  =  upper.CL*100), width =  0.3, size  =  1, color="#282728") + 
+  theme(axis.title = element_text(size=20, color="#282728", face="bold"), 
+        axis.text.x = element_text(size=18, angle=0, hjust=1,
+                                   color="#282728"), 
+        axis.text.y = element_text(size=18, color="#282728"),
+        plot.title = element_text(size=30, face="bold", hjust = 1, 
+                                    color="#c5050c"), 
+        strip.text = element_text(size=25, face="bold", color="#282728"),          strip.background =element_rect(fill="#dadfe1")) + 
+  geom_hline(yintercept=90, linetype="dashed", color="#c5050c", size=1.2, show.legend = TRUE) +
+  ylim(0,100) +
+  ggsave("Figure2.pdf", width=18, height=9, dpi=600)
+```
+
 ## Yield

### 2021-09-14 paper.Rmd
as

---
title: "paper"
author: "Maxwel Coura Oliveira"
date: "9/10/2021"
output: html_document
---

```{r}
library(tidyverse)
library(emmeans)
library(glmmTMB)
library(ggtext)
library(lme4)
library(tidymodels)
library(lmerTest)
library(ggthemes)
library(ggrepel)
```

```{r}
library(rstanarm)
library(brms)
library(bayestestR)
library(BayesFactor)
```

# Load dataset

```{r echo=TRUE, message=FALSE, warning=FALSE}
data <- read_csv("SB12.csv")
```

```{r}
glimpse(data)
```

```{r}
new_dt <- 
  data %>% 
  rename (herbicide = other) %>% 
  mutate(
    wt_14 = waterhempcontrol_14/100,
    wt_28 = waterhempcontrol_28/100,
    yield_kg = yield_bu * 67.5) %>% 
  mutate(
    wt_14 = 
      case_when(
        waterhempcontrol_14 == 100   ~  0.99,
        TRUE            ~ wt_14),
    wt_28 = case_when(
        waterhempcontrol_28 == 100   ~  0.99,
        waterhempcontrol_28 == 0   ~  0.01,
        TRUE            ~ wt_28)) %>% 
  filter(
    herbicide != "PRE only"
  ) %>% 
  mutate_if(is_character, as.factor) %>% 
  mutate(rep = as.factor(rep),
         year = as.factor(year))
```

# 14 DAT

```{r}
model1 <- brm(wt_14 ~ herbicide +
                (1|rep/location/year),
                  family = Beta(link = "logit", link_phi = "log"),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 15),
               prior = set_prior("student_t(0.1, 0.5, 2)", 
                                 class = "b"),
#                                 seed = 1235,
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

```{r}
summary(model1)
```

```{r}
epred1 <- emmeans(model1, "herbicide", epred = TRUE, cont="pairwise")
```

```{r}
w14_main <- pairs(emmeans(model1, ~ herbicide))

describe_posterior(w14_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model1)
```

```{r}
epred1$emmeans %>% 
  as_tibble() %>% 
  mutate(DAT = "14 DAT") -> epred1_1
```

# 28 DAT

```{r}
model2 <- brm(wt_28 ~ herbicide +
                (1|rep/location/year),
                  family = Beta(link = "logit", link_phi = "log"),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999),
               prior = set_prior("student_t(0.1, 0.5, 2)", 
                                 class = "b"),
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

```{r}
summary(model2)
```

```{r}
epred2 <- emmeans(model2, "herbicide", epred = TRUE, cont="pairwise")
```

```{r}
w28_main <- pairs(emmeans(model2, ~ herbicide))

describe_posterior(w28_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model2)
```

```{r}
epred2$emmeans %>% 
  as_tibble() %>% 
  mutate(DAT = "28 DAT") -> epred2_2
```

# Figures

```{r}
epred1_1 %>% 
  bind_rows(epred2_2) %>% 
  mutate(herbicide = fct_recode(herbicide,
                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor")) -> epred_wt
```

```{r}
epred_wt %>% 
ggplot(aes(x = fct_reorder(herbicide, emmean), 
           y = emmean * 100, color = herbicide)) +
  geom_point(size = 2) +
  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
                 size = 1.2) +
  coord_flip() +
  facet_grid(~ DAT) +
  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
                    force_pull = 0,
                    direction = "y",
                    point.padding = NA,
                    min.segment.length = 14,
                    vjust = 0.5,
                    position = position_dodge2(width = 0.4),
                    seed = 465) +
  scale_color_brewer(palette = "Set1") +
  ylim(0, 100) +
  labs(x = NULL, y = "Waterhemp control (%)") +
  theme_bw() +
  theme(axis.text.y = element_markdown(),
        strip.text = element_markdown(size = 11),
        legend.position = "none")

ggsave("figures/Figure 1.png", width = 9)
```

# Yield

```{r}
new_dt %>% 
  ggplot(aes(x = herbicide,  y = yield_kg)) +
  geom_boxplot() +
  ylim(0, 5500)
```

```{r}
model4 <- brm(yield_kg ~ herbicide +
                (1|rep/location/year), 
                  family = gaussian(),
               warmup = 1000, iter = 2000, chains = 4, 
              control = list(adapt_delta = 0.999, max_treedepth = 15),
               prior = set_prior("normal(0, 2)", 
                                 class = "b"),
                  data = new_dt, save_pars = save_pars(all = TRUE))
```

```{r}
summary(model4)
```

```{r}
epred4 <- emmeans(model4, "herbicide", epred = TRUE, cont="pairwise")
```

```{r}
yield_main <- pairs(emmeans(model4, ~ herbicide))

describe_posterior(yield_main,
                   centrality = "mean", dispersion = TRUE,
                   ci = .95, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = model4)
```

### 2021-09-14 soyherb.Rmd
Update soyherb.Rmd
as

--- 2020-10-28 soyherb.Rmd
@@
 
+```{r}
+view(data)
+```
+
 # Data visualization
@@
 ```{r fig.align='center'}
-ggplot(data, aes(x=reorder(other,waterhempcontrol_14), y=waterhempcontrol_14,
+ggplot(data, aes(x = reorder(other,waterhempcontrol_14), 
+                 y = waterhempcontrol_14,
        fill=trade, color=trade)) +
@@
   coord_flip() +
+  ylim(0, 100) +
   labs(x="", y="Waterhemp control (%)") +
@@
   coord_flip() +
+  ylim(0, 100) +
   labs(x="", y="Weed biomass (g m2)") +
@@
 ```{r message=FALSE, warning=FALSE}
-model_14 <- glmmTMB(wt_14 ~ herbicide * location * year + (1|rep), beta_family(link = "logit"), data=new_dt)
+model_14 <- glmmTMB(wt_14 ~ herbicide * location * year + 
+                      (1|rep), 
+                    beta_family(link = "logit"), data=new_dt)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-model_14_2 <- glmmTMB(wt_14 ~ herbicide + (1|rep) + (1|location/year), beta_family(link = "logit"), data=new_dt)
+model_14_2 <- glmmTMB(wt_14 ~ herbicide + (1|rep) + 
+                        (1|location/year), beta_family(link = "logit"), 
+                      data=new_dt)
 ```
@@
 ```{r }
-lsmeans_14<- emmeans(model_14_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
+lsmeans_14 <- emmeans(model_14_2, ~ herbicide, cont="pairwise", 
+                      adjust="none", type="response", alpha=0.05)
 ```
@@
 ```{r fig.align='center'}
-plot(lsmeans_14, ~ herbicide, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
+plot(lsmeans_14, ~ herbicide, comparisons=TRUE, type="response", 
+     alpha=0.05, adjust="none") + xlim(0, 1)
 ```
@@
 ```{r message=FALSE, warning =FALSE}
-CLD(lsmeans_14$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
+multcomp::cld(lsmeans_14$emmeans, alpha=0.05, Letters=letters, 
+    adjust="none", 
+    reversed = TRUE) %>%
   kbl() %>%
@@
 ```{r message=FALSE, warning=FALSE}
-model_28 <- glmmTMB(wt_28 ~ herbicide * location * year + (1|rep), beta_family(link = "logit"), data=new_dt)
+model_28 <- glmmTMB(wt_28 ~ herbicide * location * year + (1|rep), 
+                    beta_family(link = "logit"), data=new_dt)
 ```
@@
 ```{r message=FALSE, warning=FALSE}
-model_28_2 <- glmmTMB(wt_28 ~ herbicide + (1|rep) + (1|location/year), beta_family(link = "logit"), data=new_dt)
+model_28_2 <- glmmTMB(wt_28 ~ herbicide + (1|rep) + (1|location/year),
+                      beta_family(link = "logit"), data=new_dt)
 ```
@@
 ```{r }
-lsmeans_28 <- emmeans(model_28_2, ~ herbicide, cont="pairwise", adjust="none", type="response", alpha=0.05)
+lsmeans_28 <- emmeans(model_28_2, ~ herbicide, cont="pairwise", 
+                      adjust="none", type="response", alpha=0.05)
 ```
@@
 ```{r fig.align='center'}
-plot(lsmeans_28, ~ herbicide, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
+plot(lsmeans_28, ~ herbicide, comparisons=TRUE, type="response", 
+     alpha=0.05, adjust="none") + xlim(0,1)
 ```
@@
 ```{r message=FALSE, warning =FALSE}
-CLD(lsmeans_28$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
+multcomp::cld(lsmeans_28$emmeans, alpha=0.05, Letters=letters, 
+    adjust="none", reversed = TRUE) %>%
   kbl() %>%
@@
 }
+```
+
+```{r}
+nd14 <- data.frame(lsmeans_14$emmeans) %>% 
+  mutate(dat = "14 DAT")
+nd28 <- data.frame(lsmeans_28$emmeans)  %>% 
+  mutate(dat = "28 DAT")
+nd <- bind_rows(nd14, nd28)
+
+nd %>% 
+  mutate(herbicide = fct_relevel(herbicide, c("PRE fb glufosinate",
+                    "PRE fb glufosinate + acetochlor",
+                    "PRE fb glufosinate + dimethenamid-P",
+                    "PRE fb glufosinate + S-metolachlor",
+                    "PRE fb glufosinate + imazethapyr",
+                    "PRE fb glufosinate + fomesafen",
+                    "PRE fb glufosinate + pyroxasulfone",
+                    "PRE fb glufosinate + fomesafen + acetochlor",
+                    "PRE fb glufosinate + fomesafen + S-metolachlor"))) %>%
+ggplot(aes(x=herbicide, response, y=response*100)) + 
+  facet_wrap(~dat) +
+  coord_flip() + 
+  geom_point(size=3, color="#282728") + 
+  theme_bw() +  
+  labs(y="Waterhemp control (%)", x="", title="") +
+  geom_errorbar(aes(ymin  =  lower.CL*100, ymax  =  upper.CL*100), width =  0.3, size  =  1, color="#282728") + 
+  theme(axis.title = element_text(size=20, color="#282728", face="bold"), 
+        axis.text.x = element_text(size=18, angle=0, hjust=1,
+                                   color="#282728"), 
+        axis.text.y = element_text(size=18, color="#282728"),
+        plot.title = element_text(size=30, face="bold", hjust = 1, 
+                                    color="#c5050c"), 
+        strip.text = element_text(size=25, face="bold", color="#282728"),          strip.background =element_rect(fill="#dadfe1")) + 
+  geom_hline(yintercept=90, linetype="dashed", color="#c5050c", size=1.2, show.legend = TRUE) +
+  ylim(0,100)
+
+ggsave("figures/Figure2.png", width=18, height=9, dpi=600)
 ```
@@
 ```{r fig.align='center'}
-plot(lsmeans_fit, ~ siteyr, comparisons=TRUE, type="response", alpha=0.05, adjust="none")
+plot(lsmeans_fit, ~ siteyr, comparisons=TRUE, type="response", 
+     alpha=0.05, adjust="none")
 ```
@@
 ```{r message=FALSE, warning =FALSE}
-CLD(lsmeans_fit$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
+multcomp::cld(lsmeans_fit$emmeans, alpha=0.05, Letters=letters, adjust="none", reversed = TRUE) %>%
   kbl() %>%

### 2021-09-14 paper.Rmd
bbnb

@@
                warmup = 1000, iter = 2000, chains = 4, 
-              control = list(adapt_delta = 0.999, max_treedepth = 15),
-               prior = set_prior("student_t(0.1, 0.5, 2)", 
+              control = list(adapt_delta = 0.999, max_treedepth = 11),
+               prior = set_prior("student_t(0.1, 0.5, 8)", 
                                  class = "b"),
-#                                 seed = 1235,
+              seed = 1234,
                   data = new_dt, save_pars = save_pars(all = TRUE))
@@
                warmup = 1000, iter = 2000, chains = 4, 
-              control = list(adapt_delta = 0.999),
-               prior = set_prior("student_t(0.1, 0.5, 2)", 
+              control = list(adapt_delta = 0.999, max_treedepth = 11),
+               prior = set_prior("student_t(0.1, 0.5, 8)", 
                                  class = "b"),
+              seed = 1234,
                   data = new_dt, save_pars = save_pars(all = TRUE))
@@
 
+```{r}
+model3 <- brm(biomass_gm2 ~ herbicide +
+                (1|rep/location/year), 
+                  family = gaussian(),
+               warmup = 1000, iter = 2000, chains = 4, 
+              control = list(adapt_delta = 0.999, max_treedepth = 11),
+               prior = set_prior("student_t(0.1, 1, 8)", 
+                                 class = "b"),
+              seed = 1234,
+                  data = new_dt, save_pars = save_pars(all = TRUE))
+```
+
+```{r}
+summary(model3)
+```
+
+```{r}
+new_dt %>% 
+  group_by(herbicide) %>% 
+  summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
+            counts = sd(biomass_gm2, na.rm = TRUE))
+```
+
+```{r}
+epred3 <- emmeans(model3, "herbicide", epred = TRUE, cont="pairwise")
+```
+
+```{r}
+yield_main <- pairs(emmeans(model4, ~ herbicide))
+
+describe_posterior(yield_main,
+                   centrality = "mean", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model4)
+```
+
 # Figures
@@
   mutate(herbicide = fct_recode(herbicide,
-                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor")) -> epred_wt
+                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor")) %>% 
+  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred_wt
 ```
@@
                     seed = 465) +
-  scale_color_brewer(palette = "Set1") +
+#  scale_color_brewer(palette = "Set1") +
+  scale_color_calc() +
   ylim(0, 100) +
@@
   theme(axis.text.y = element_markdown(),
-        strip.text = element_markdown(size = 11),
+        strip.text = element_markdown(size = 11, face = "bold"),
         legend.position = "none")
 
-ggsave("figures/Figure 1.png", width = 9)
+ggsave("figures/Figure 2.png", width = 9)
 ```
@@
 ```{r}
-model4 <- brm(yield_kg ~ herbicide +
+model4 <- brm(yield_bu ~ herbicide +
                 (1|rep/location/year), 
@@
                warmup = 1000, iter = 2000, chains = 4, 
-              control = list(adapt_delta = 0.999, max_treedepth = 15),
-               prior = set_prior("normal(0, 2)", 
+              control = list(adapt_delta = 0.999, max_treedepth = 11),
+               prior = set_prior("student_t(0.1, 2, 8)", 
                                  class = "b"),
+              seed = 1234,
                   data = new_dt, save_pars = save_pars(all = TRUE))
@@
 summary(model4)
+```
+
+```{r}
+new_dt %>% 
+  group_by(herbicide) %>% 
+  summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
+            counts = mean(counts_m2, na.rm = TRUE))
 ```
@@
 ```
+
+```{r}
+epred4$emmeans |> as_tibble() %>% 
+ggplot(aes(x = fct_reorder(herbicide, emmean), 
+           y = emmean, color = herbicide)) +
+  geom_point(size = 2) +
+  geom_linerange(aes(ymin = lower.HPD, ymax = upper.HPD),
+                 size = 1.2) +
+  coord_flip() +
+  geom_text_repel(aes(label = round(emmean,1)), size = 3.5,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_dodge2(width = 0.4),
+                    seed = 465) +
+  scale_color_brewer(palette = "Set1") +
+  ylim(0, 100) +
+  labs(x = NULL, y = "Waterhemp control (%)") +
+  theme_bw() +
+  theme(axis.text.y = element_markdown(),
+        strip.text = element_markdown(size = 11),
+        legend.position = "none")
+
+ggsave("figures/Figure 3.png", width = 9)
+```

### 2021-09-14 paper.Rmd
as

@@
 new_dt %>% 
-  group_by(herbicide) %>% 
+  group_by(herbicide, location) %>% 
   summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
-            counts = sd(biomass_gm2, na.rm = TRUE))
+            sd = sd(biomass_gm2, na.rm = TRUE)) %>% 
+  filter(location == "Brooklyn")
 ```

### 2021-09-28 paper.Rmd
nbn

--- 2021-09-14 paper.Rmd
@@
 ```{r}
-epred2 <- emmeans(model2, "herbicide", epred = TRUE, cont="pairwise")
+epred2 <- emmeans(model2, "herbicide", 
+                  epred = TRUE, 
+                  cont="pairwise"
+                  )
 ```
@@
 describe_posterior(w28_main,
-                   centrality = "mean", dispersion = TRUE,
+                   centrality = "median", dispersion = TRUE,
                    ci = .95, ci_method = "hdi",
@@
 
-```{r}
-model3 <- brm(biomass_gm2 ~ herbicide +
-                (1|rep/location/year), 
-                  family = gaussian(),
-               warmup = 1000, iter = 2000, chains = 4, 
-              control = list(adapt_delta = 0.999, max_treedepth = 11),
-               prior = set_prior("student_t(0.1, 1, 8)", 
-                                 class = "b"),
-              seed = 1234,
-                  data = new_dt, save_pars = save_pars(all = TRUE))
-```
-
-```{r}
-summary(model3)
-```
-
-```{r}
-new_dt %>% 
-  group_by(herbicide) %>% 
-  summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
-            counts = sd(biomass_gm2, na.rm = TRUE))
-```
-
-```{r}
-epred3 <- emmeans(model3, "herbicide", epred = TRUE, cont="pairwise")
-```
-
-```{r}
-yield_main <- pairs(emmeans(model4, ~ herbicide))
-
-describe_posterior(yield_main,
-                   centrality = "mean", dispersion = TRUE,
-                   ci = .95, ci_method = "hdi",
-                   test = c("bayesfactor"),
-                   bf_prior = model4)
-```
-
 # Figures
@@
   mutate(herbicide = fct_recode(herbicide,
-                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor")) %>% 
+                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
+                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
   mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred_wt
@@
 ```{r}
-epred_wt %>% 
-ggplot(aes(x = fct_reorder(herbicide, emmean), 
+epred_wt |> 
+  mutate(herbicide = fct_relevel(herbicide,
+                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
+                                            "glufosinate + imazethapyr", 
+                                            "glufosinate + *S*-metolachlor",
+                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
+                                            "glufosinate + fomesafen + acetochlor",
+                                            "glufosinate + fomesafen + *S*-metolachlor",
+                                            "glufosinate + fomesafen"))) -> epred_wt1
+```
+
+```{r}
+epred_wt1 %>% 
+ggplot(aes(x = herbicide, 
            y = emmean * 100, color = herbicide)) +
@@
         strip.text = element_markdown(size = 11, face = "bold"),
-        legend.position = "none")
+        legend.position = "none") -> fig1
 
@@
 new_dt %>% 
-  ggplot(aes(x = herbicide,  y = yield_kg)) +
+  ggplot(aes(x = herbicide,  y = yield_bu)) +
   geom_boxplot() +
-  ylim(0, 5500)
+  ylim(0, 70) +
+  coord_flip()
+```
+
+```{r}
+new_dt %>% 
+  group_by(herbicide) |> 
+  summarise(yield = mean(yield_bu, na.rm = TRUE),
+            sd = sd(yield_bu, na.rm = TRUE))
 ```
@@
 ```{r}
-epred4 <- emmeans(model4, "herbicide", epred = TRUE, cont="pairwise")
+epred4 <- emmeans(model4, "herbicide", epred = TRUE,
+                  #cont="pairwise"
+                  )
+epred4
 ```
@@
 describe_posterior(yield_main,
-                   centrality = "mean", dispersion = TRUE,
+                   centrality = "median", dispersion = TRUE,
                    ci = .95, ci_method = "hdi",
@@
 ```{r}
-epred4$emmeans |> as_tibble() %>% 
-ggplot(aes(x = fct_reorder(herbicide, emmean), 
+epred4 |> as_tibble() %>% 
+  mutate(herbicide = fct_recode(herbicide,
+                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
+                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
+  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred4_wt
+```
+
+```{r}
+epred4_wt %>% 
+  mutate(herbicide = fct_relevel(herbicide,
+                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
+                                            "glufosinate + imazethapyr", 
+                                            "glufosinate + *S*-metolachlor",
+                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
+                                            "glufosinate + fomesafen", 
+                                            "glufosinate + fomesafen + acetochlor",
+                                            "glufosinate + fomesafen + *S*-metolachlor"))) -> epred4_wt1
+```
+
+```{r}
+epred4_wt1 %>% 
+ggplot(aes(x = herbicide, 
            y = emmean, color = herbicide)) +
@@
         strip.text = element_markdown(size = 11),
-        legend.position = "none")
+        legend.position = "none") -> fig2
 
@@
 ```
+
+```{r}
+library(patchwork)
+```
+
+```{r}
+fig1 + fig2
+
+ggsave("figures/Figure 4.png", width = 9)
+```

### 2021-10-05 paper.Rmd
AS

@@
 ```{r}
-epred_wt1 %>% 
-ggplot(aes(x = herbicide, 
+epred_wt %>% 
+ggplot(aes(x = fct_reorder(herbicide, emmean),
            y = emmean * 100, color = herbicide)) +
@@
                     vjust = 0.5,
-                    position = position_dodge2(width = 0.4),
+                    position = position_nudge_repel(x = 0.3),
                     seed = 465) +
@@
         strip.text = element_markdown(size = 11, face = "bold"),
-        legend.position = "none") -> fig1
+        legend.position = "none",
+        plot.background = element_rect(fill = "#F5F5F5"),
+        panel.background = element_rect(fill = "#F5F5F5"),
+        axis.text = element_markdown(color = "#333333")) -> fig1
 
-ggsave("figures/Figure 2.png", width = 9)
+ggsave("figures/Figure 2.png", width = 8, height = 4)
 ```
@@
 ```
+```{r}
+epred4_wt1 %>%
+  mutate(herbicide = fct_relevel(herbicide,
+                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
+                                            "glufosinate + imazethapyr", 
+                                            "glufosinate + *S*-metolachlor",
+                                            "glufosinate + pyroxasulfone", 
+                                            "glufosinate + acetochlor", "glufosinate + fomesafen",
+                                            "glufosinate + fomesafen + acetochlor",
+                                            "glufosinate + fomesafen + *S*-metolachlor"))) -> epred4_wt1
+```
 
 ```{r}
-epred4_wt1 %>% 
-ggplot(aes(x = herbicide, 
+epred4_wt %>%
+  ggplot(aes(x = fct_reorder(herbicide, emmean),
            y = emmean, color = herbicide)) +
@@
                     vjust = 0.5,
-                    position = position_dodge2(width = 0.4),
+                    position = position_nudge_repel(x = 0.3),
                     seed = 465) +
-  scale_color_brewer(palette = "Set1") +
-  ylim(0, 100) +
-  labs(x = NULL, y = "Waterhemp control (%)") +
+  scale_color_calc() +
+  scale_y_continuous(limits = c(0,75), breaks = seq(0, 75, 15)) +
+  labs(x = NULL, y = expression(paste("Soybean yield (bu acre"^"-1",")"))) +
   theme_bw() +
@@
         strip.text = element_markdown(size = 11),
-        legend.position = "none") -> fig2
+        legend.position = "none",
+        plot.background = element_rect(fill = "#F5F5F5"),
+        panel.background = element_rect(fill = "#F5F5F5"),
+        axis.text = element_markdown(color = "#333333")) -> fig2
 
-ggsave("figures/Figure 3.png", width = 9)
+ggsave("figures/Figure 3.png", width = 6, height = 4)
 ```

### 2021-10-05 tables.Rmd
AS

---
title: "tables"
author: "Maxwel Coura Oliveira"
date: "10/5/2021"
output: html_document
---

```{r}
library(tidyverse)
library(gtExtras)
library(gt)
```

```{r}
tables <- read_csv("tables.csv")
```

```{r}
tables %>%
  mutate_if(is.double, ~round(.,2)) |> 
  gt() %>% 
  gt_theme_espn() |> 
  tab_spanner(
    label = "Bayes Factor",
    columns = c(`14 DAT`:Yield)) |> 
    tab_footnote(
      footnote = "DAT, Days After Treatment - Waterhemp control",
      locations = cells_column_labels(
      columns = c(`14 DAT`,`28 DAT`)
    )) |> 
  gt_highlight_rows(rows = c(1,3:5,7), 
                    font_weight = "bold", 
                    fill = "#f8ff00")  -> fig_tab#|> 
#  gt_hulk_col_numeric(`14 DAT`:Yield, reverse = FALSE, trim = TRUE)

gtsave(fig_tab, "figures/Figure 3.png")
```

```{r}
bayes <- read_csv("bayes1.csv")
```

```{r}
bayes |> 
  gt() %>% 
  gt_theme_espn() -> fig_tab1

gtsave(fig_tab1, "figures/Figure 1.png")
```

### 2021-10-05 tables.Rmd
as

@@
   mutate_if(is.double, ~round(.,2)) |> 
+#  mutate(Parameter = fct_recode(Parameter,
+#                                "glufosinate vs glufosinate + <i>S</i>-metolachlor" = "glufosinate vs glufosinate + S-metolachlor")) |> 
   gt() %>% 
@@
                     font_weight = "bold", 
-                    fill = "#f8ff00")  -> fig_tab#|> 
+                    fill = "beige")  -> fig_tab#|> 
 #  gt_hulk_col_numeric(`14 DAT`:Yield, reverse = FALSE, trim = TRUE)

### 2021-10-07 paper.Rmd
AS
as

@@
     wt_28 = waterhempcontrol_28/100,
+    wt_hv = waterhempcontrol_harvest/100,
     yield_kg = yield_bu * 67.5) %>% 
@@
 
+# Harvest
+
+```{r}
+model5 <- brm(wt_hv ~ herbicide +
+                (1|rep/location/year),
+                  family = Beta(link = "logit", link_phi = "log"),
+               warmup = 1000, iter = 2000, chains = 4, 
+              control = list(adapt_delta = 0.999, max_treedepth = 11),
+               prior = set_prior("student_t(0.1, 0.5, 8)", 
+                                 class = "b"),
+              seed = 1234,
+                  data = new_dt, save_pars = save_pars(all = TRUE))
+```
+
+```{r}
+summary(model5)
+```
+
+```{r}
+epred5 <- emmeans(model5, "herbicide", epred = TRUE) |> 
+  as_tibble() %>% 
+  mutate(DAT = "Harvest")
+```
+
+```{r}
+whv_main <- pairs(emmeans(model5, ~ herbicide))
+
+describe_posterior(whv_main,
+                   centrality = "mean", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model5)
+```
+
 # Figures
@@
   bind_rows(epred2_2) %>% 
+  bind_rows(epred5) |> 
   mutate(herbicide = fct_recode(herbicide,
@@
 
-ggsave("figures/Figure 3.png", width = 6, height = 4)
+ggsave("figures/Figure 4.png", width = 6, height = 4)
+```
+
+## Biomass
+
+```{r}
+new_dt |> 
+  ungroup() |> 
+  dplyr::mutate(location, year, herbicide, rep, biomass_gm2) |> 
+  filter(!is.na(biomass_gm2)) -> biomass
 ```
@@
 ```{r}
-library(patchwork)
+model3 <- brm(biomass_gm2 ~ herbicide +
+                (1|rep/location), 
+                  family = gaussian(),
+               warmup = 1000, iter = 2000, chains = 4, 
+              control = list(adapt_delta = 0.999, max_treedepth = 11),
+               prior = set_prior("student_t(0.1, 2, 8)", 
+                                 class = "b"),
+              seed = 1234,
+                  data = new_dt, save_pars = save_pars(all = TRUE))
 ```
@@
 ```{r}
-fig1 + fig2
+epred3 <- emmeans(model3, "herbicide", epred = TRUE,
+                  #cont="pairwise"
+                  )
+epred3
+```
 
-ggsave("figures/Figure 4.png", width = 9)
+```{r}
+biomass_main <- pairs(emmeans(model3, ~ herbicide))
+
+describe_posterior(biomass_main,
+                   centrality = "median", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model3)
 ```
+
+```{r}
+mod_3 <- lmer(biomass_gm2 ~ herbicide +
+                (1|rep/location),
+                  data = new_dt)
+```
+
+```{r}
+anova(mod_3)
+```

### 2021-10-08 Weather.Rmd
kl

---
title: "Weather"
author: "Maxwel Coura Oliveira"
date: "10/7/2021"
output: html_document
---

```{r}
library(tidyverse) # Data wrangling
library(lubridate) # Dates operations
library(daymetr)
library(chirps)
library(patchwork)
library(ggtext)
library(nasapower)
library(vegan)
```

```{r}
# your data
df_time <- tibble(ID = c('1','2'), 
                  Site = c('Lancaster','Brooklyn'),
                  # Both coordinates in decimal format
                  latitude = c(42.83, 42.52),
                  longitude = c(-90.76, -89.23),
                  Start = c('1989-01-01','1989-01-01'),
                  End = c('2020-12-31','2020-12-31')) %>% 
            mutate_at(5:6, ymd) # as date
```

## Daymet

```{r function}
source("weather_daymet.R")
```

```{r get_data}
#dpp default = 0 - dpp = days prior start date
df_daymet <- weather_daymet(input = df_time, dpp = 0) 
```

```{r}
df_daymet %>% 
  janitor::clean_names() %>% 
  mutate(month_lab = month(date, label = TRUE)) -> weather
```

```{r}
weather %>% 
  filter(month %in% c(5, 6, 7, 8, 9, 10)) %>% 
  mutate(year = as.character(year),
         highlight = ifelse(year %in% c("2019", "2020"), TRUE, FALSE),
         variable = if_else(highlight == TRUE, year, "NA")) -> weather1
```

```{r}
weather1 %>% 
  filter(year %in% c(2019, 2020)) %>% 
  group_by(site, year, month) %>% 
  summarise(prec = sum(pp), tmax = mean(tmax), tmin = mean(tmin), tmean = mean(tmean)) %>% 
  mutate_if(is.double, ~round(., 1)) -> weather2
```

```{r}
weather2 |> 
  group_by(month) |> 
  summarise(tmean = mean(tmean))
```

### 2021-10-08 paper.Rmd
kl

@@
 library(ggrepel)
+library(tidytext)
 ```
@@
 
+```{r}
+new_dt |> 
+  ggplot(aes(x = herbicide, y = waterhempcontrol_harvest)) +
+  geom_boxplot() +
+  coord_flip() +
+  geom_jitter() +
+  facet_grid(year ~ location)
+```
+
+```{r}
+new_dt |> 
+  ggplot(aes(x = herbicide, y = waterhempcontrol_harvest)) +
+  geom_boxplot() +
+  coord_flip() +
+  geom_jitter() +
+  facet_grid(year ~ location)
+```
+
 # 14 DAT
@@
   mutate(DAT = "14 DAT") -> epred1_1
+```
+
+```{r}
+epred1_1 %>% 
+  mutate(herbicide = fct_recode(herbicide,
+                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
+                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
+  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred1_11
+```
+
+```{r}
+epred1_11 |> 
+  mutate(herbicide = fct_relevel(herbicide,
+                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
+                                            "glufosinate + imazethapyr", 
+                                            "glufosinate + *S*-metolachlor",
+                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
+                                            "glufosinate + fomesafen + acetochlor",
+                                            "glufosinate + fomesafen + *S*-metolachlor",
+                                            "glufosinate + fomesafen"))) |> 
+  mutate(emmean = round(emmean, 2)) -> epred1_111
+```
+
+```{r}
+epred1_111 %>% 
+ggplot(aes(x = fct_reorder(herbicide, emmean),
+           y = emmean * 100, color = herbicide)) +
+  geom_point(size = 2) +
+  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
+                 size = 1.2) +
+  coord_flip() +
+  facet_grid(~ DAT) +
+  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_nudge_repel(x = 0.3),
+                    seed = 465) +
+#  scale_color_brewer(palette = "Set1") +
+  scale_color_calc() +
+  ylim(0, 100) +
+  labs(x = NULL, y = "Waterhemp control (%)") +
+  theme_bw() +
+  theme(axis.text.y = element_markdown(),
+        axis.title.x = element_blank(),
+        strip.text = element_markdown(size = 11, face = "bold"),
+        legend.position = "none",
+        plot.background = element_rect(fill = "#F5F5F5"),
+        panel.background = element_rect(fill = "#F5F5F5"),
+        axis.text = element_markdown(color = "#333333")) -> fig1
+
+ggsave("figures/Figure 2.png", width = 5, height = 4)
 ```
@@
 
+```{r}
+epred2_2 %>% 
+  mutate(herbicide = fct_recode(herbicide,
+                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
+                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
+  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred2_22
+```
+
+```{r}
+epred2_22|> 
+  mutate(herbicide = fct_relevel(herbicide,
+                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
+                                            "glufosinate + imazethapyr", 
+                                            "glufosinate + *S*-metolachlor",
+                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
+                                            "glufosinate + fomesafen + acetochlor",
+                                            "glufosinate + fomesafen + *S*-metolachlor",
+                                            "glufosinate + fomesafen"))) |> 
+  mutate(emmean = round(emmean, 2)) -> epred2_222
+```
+
+```{r}
+epred2_222 %>% 
+ggplot(aes(x = fct_reorder(herbicide, emmean),
+           y = emmean * 100, color = herbicide)) +
+  geom_point(size = 2) +
+  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
+                 size = 1.2) +
+  coord_flip() +
+  facet_grid(~ DAT) +
+  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_nudge_repel(x = 0.3),
+                    seed = 465) +
+#  scale_color_brewer(palette = "Set1") +
+  scale_color_calc() +
+  ylim(0, 100) +
+  labs(x = NULL, y = "Waterhemp control (%)") +
+  theme_bw() +
+  theme(axis.text.y = element_markdown(),
+        axis.title.x = element_blank(),
+        strip.text = element_markdown(size = 11, face = "bold"),
+        legend.position = "none",
+        plot.background = element_rect(fill = "#F5F5F5"),
+        panel.background = element_rect(fill = "#F5F5F5"),
+        axis.text = element_markdown(color = "#333333")) -> fig2
+
+ggsave("figures/Figure 22.png", width = 5, height = 4)
+```
+
 # Harvest
@@
                    bf_prior = model5)
+```
+
+```{r}
+epred5 %>% 
+  mutate(herbicide = fct_recode(herbicide,
+                                "PRE fb glufosinate + fomesafen + *S*-metolachlor" = "PRE fb glufosinate + fomesafen + S-metolachlor",
+                                "PRE fb glufosinate + *S*-metolachlor" = "PRE fb glufosinate + S-metolachlor")) %>% 
+  mutate(herbicide = str_remove(herbicide, "PRE fb ")) -> epred55
+```
+
+```{r}
+epred55 |> 
+  mutate(herbicide = fct_relevel(herbicide,
+                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
+                                            "glufosinate + imazethapyr", 
+                                            "glufosinate + *S*-metolachlor",
+                                            "glufosinate + pyroxasulfone", "glufosinate + acetochlor",
+                                            "glufosinate + fomesafen + acetochlor",
+                                            "glufosinate + fomesafen + *S*-metolachlor",
+                                            "glufosinate + fomesafen"))) |> 
+  mutate(emmean = round(emmean, 2)) -> epred555
+```
+
+```{r}
+epred555 %>% 
+ggplot(aes(x = fct_reorder(herbicide, emmean),
+           y = emmean * 100, color = herbicide)) +
+  geom_point(size = 2) +
+  geom_linerange(aes(ymin = lower.HPD * 100, ymax = upper.HPD * 100),
+                 size = 1.2) +
+  coord_flip() +
+  facet_grid(~ DAT) +
+  geom_text_repel(aes(label = round(emmean*100,1)), size = 3.5,
+                    force_pull = 0,
+                    direction = "y",
+                    point.padding = NA,
+                    min.segment.length = 14,
+                    vjust = 0.5,
+                    position = position_nudge_repel(x = 0.3),
+                    seed = 465) +
+#  scale_color_brewer(palette = "Set1") +
+  scale_color_calc() +
+  ylim(0, 100) +
+  labs(x = NULL, y = "Waterhemp control (%)") +
+  theme_bw() +
+  theme(axis.text.y = element_markdown(),
+        strip.text = element_markdown(size = 11, face = "bold"),
+        legend.position = "none",
+        plot.background = element_rect(fill = "#F5F5F5"),
+        panel.background = element_rect(fill = "#F5F5F5"),
+        axis.text = element_markdown(color = "#333333")) -> fig3
+
+#ggsave("figures/Figure 222.png", width = 5, height = 4)
+```
+
+```{r}
+library(patchwork)
+```
+
+```{r}
+fig1 / fig2 / fig3 +
+  plot_annotation(tag_levels = 'A')
+
+ggsave("figures/Figure 2.png", width = 6, height = 12)
 ```
@@
         panel.background = element_rect(fill = "#F5F5F5"),
-        axis.text = element_markdown(color = "#333333")) -> fig1
+        axis.text = element_markdown(color = "#333333"))
 
-ggsave("figures/Figure 2.png", width = 8, height = 4)
+#ggsave("figures/Figure 2.png", width = 9, height = 4)
 ```
@@
 ```{r}
-new_dt %>% 
-  group_by(herbicide) %>% 
-  summarise(biomass = mean(biomass_gm2, na.rm = TRUE),
-            counts = mean(counts_m2, na.rm = TRUE))
-```
-
-```{r}
-epred4 <- emmeans(model4, "herbicide", epred = TRUE,
-                  #cont="pairwise"
-                  )
-epred4
-```
-
-```{r}
 yield_main <- pairs(emmeans(model4, ~ herbicide))
@@
 ```
+
 ```{r}
 epred4_wt1 %>%
-  mutate(herbicide = fct_relevel(herbicide,
-                                 levels = c("glufosinate", "glufosinate + dimethenamid-P",
-                                            "glufosinate + imazethapyr", 
-                                            "glufosinate + *S*-metolachlor",
-                                            "glufosinate + pyroxasulfone", 
-                                            "glufosinate + acetochlor", "glufosinate + fomesafen",
-                                            "glufosinate + fomesafen + acetochlor",
-                                            "glufosinate + fomesafen + *S*-metolachlor"))) -> epred4_wt1
-```
-
-```{r}
-epred4_wt %>%
   ggplot(aes(x = fct_reorder(herbicide, emmean),
@@
 ```
+
+## Weed density
+
+```{r}
+new_dt |> 
+  ungroup() |> 
+  dplyr::select(location, year, herbicide, rep, counts_m2) |> 
+  filter(!is.na(counts_m2)) -> density
+```
+
+```{r}
+model6 <- brm(counts_m2 ~ herbicide +
+                (1|rep/location), 
+                  family = poisson(),
+               warmup = 1000, iter = 2000, chains = 4, 
+              control = list(adapt_delta = 0.999, max_treedepth = 11),
+               prior = set_prior("student_t(0.1, 2, 8)", 
+                                 class = "b"),
+              seed = 1234,
+                  data = new_dt, save_pars = save_pars(all = TRUE))
+```
+
+```{r}
+epred6 <- emmeans(model6, "herbicide", epred = TRUE,
+                  #cont="pairwise"
+                  )
+epred6
+```
+
+```{r}
+density_main <- pairs(emmeans(model6, ~ herbicide))
+
+describe_posterior(density_main,
+                   centrality = "median", dispersion = TRUE,
+                   ci = .95, ci_method = "hdi",
+                   test = c("bayesfactor"),
+                   bf_prior = model6)
+```

### 2021-10-08 Weather.Rmd
mnm

@@
 library(ggtext)
+library(ggthemes)
 library(nasapower)
+library(ggdist)
 library(vegan)
@@
 weather1 %>% 
-  filter(year %in% c(2019, 2020)) %>% 
-  group_by(site, year, month) %>% 
+#  filter(year %in% c(2019, 2020)) %>% 
+  group_by(site, year, month, month_lab) %>% 
   summarise(prec = sum(pp), tmax = mean(tmax), tmin = mean(tmin), tmean = mean(tmean)) %>% 
-  mutate_if(is.double, ~round(., 1)) -> weather2
+  mutate_if(is.double, ~round(., 1)) 
 ```
@@
 ```{r}
-weather2 |> 
-  group_by(month) |> 
-  summarise(tmean = mean(tmean))
+weather1 %>% 
+  filter(month %in% c(5, 6, 7, 8, 9, 10)) %>% 
+  mutate(year = as.character(year),
+         highlight = ifelse(year %in% c("2019", "2020"), TRUE, FALSE),
+         variable = if_else(highlight == TRUE, year, "NA")) -> weather2
 ```
+
+```{r}
+weather2 %>% 
+  filter(variable != "NA") %>% 
+  ggplot(aes(x = month_lab, y = tmean, 
+             fill = variable,
+             group = variable)) +
+  geom_jitter(data = weather3 %>% 
+                filter(variable == "NA"), show.legend = FALSE, 
+              color = "#333333", alpha = 0.1, shape = 16) +
+#   geom_jitter(position = position_dodge2(width = 0.4),
+#              color = "#333333", alpha = 1, shape = 16) +
+  stat_gradientinterval(position = position_dodge2()) +
+  scale_fill_manual(values = c("red", "blue", "#333333")) +
+  facet_grid(~ site) +
+  theme_test() +
+#  geom_curve(data = text2, 
+#             x = 2, y = 13, 
+#             xend = 2.5, yend = 16,
+#             arrow = arrow(length = unit(0.07, "inch")), 
+#             size = 0.4, curvature = -0.3, color = "gray90") + 
+  scale_y_continuous(limits = c(0, 33)) +
+  labs(x = NULL, y = "Temperature (C)") +
+  theme(legend.position = "none") -> temp
+ggsave("weather.png", height = 3, width = 6)
+```

### 2021-10-08 Weather.Rmd
nkj

@@
 library(vegan)
+#https://cran.r-project.org/web/packages/ggdist/vignettes/slabinterval.html
 ```

### 2021-10-14 Weather.Rmd
asd

@@
          highlight = ifelse(year %in% c("2019", "2020"), TRUE, FALSE),
-         variable = if_else(highlight == TRUE, year, "NA")) -> weather1
+         variable = if_else(highlight == TRUE, year, "NA")) |> 
+  mutate(temp_F = ((tmean * 9/5) + 32)) -> weather1
 ```
@@
 ```{r}
+text1 <- tibble(site = "Brooklyn")
+text2 <- tibble(site = "Lancaster")
+```
+
+```{r}
 weather2 %>% 
   filter(variable != "NA") %>% 
-  ggplot(aes(x = month_lab, y = tmean, 
+  ggplot(aes(x = month_lab, y = temp_F, 
+             color = variable,
              fill = variable,
              group = variable)) +
-  geom_jitter(data = weather3 %>% 
+  geom_jitter(data = weather2 %>% 
                 filter(variable == "NA"), show.legend = FALSE, 
-              color = "#333333", alpha = 0.1, shape = 16) +
-#   geom_jitter(position = position_dodge2(width = 0.4),
-#              color = "#333333", alpha = 1, shape = 16) +
-  stat_gradientinterval(position = position_dodge2()) +
-  scale_fill_manual(values = c("red", "blue", "#333333")) +
+              color = "#333333", alpha = 0.02, shape = 16) +
+  stat_gradientinterval(position = "dodge", fill_type = "gradient") +
+  theme_bw() +
+  geom_richtext(data = text1, aes(x = 3.4, y = 44.6), lineheight = 0.4, 
+            label = "Mean air temperature <br>in <b style='color:2;'>2019</b> and <b style='color:4;'>2020</b>", size = 2, 
+            label.color = NA, fill = NA, inherit.aes = FALSE) +
+  geom_richtext(data = text2, aes(x = 3.4, y = 50), lineheight = 0.4, 
+            label = "30 years <br>daily mean <br>air temperature", size = 2, 
+             label.color = NA, fill = NA, 
+            color = "#333333", 
+            alpha = 0.5,
+            inherit.aes = FALSE) +
+  geom_curve(data = text2, aes(x = 3.9, y = 51.8, xend = 4.5, yend = 53.6),
+             arrow = arrow(length = unit(0.05, "inch")), 
+             size = 0.4, alpha = 0.5, curvature = -0.3, color = "#000000",
+             inherit.aes = FALSE) +
+  scale_color_manual(values = c(2, 4, "#333333")) +
+  scale_fill_manual(values = c(2, 4, "#333333")) +
   facet_grid(~ site) +
-  theme_test() +
-#  geom_curve(data = text2, 
-#             x = 2, y = 13, 
-#             xend = 2.5, yend = 16,
-#             arrow = arrow(length = unit(0.07, "inch")), 
-#             size = 0.4, curvature = -0.3, color = "gray90") + 
-  scale_y_continuous(limits = c(0, 33)) +
-  labs(x = NULL, y = "Temperature (C)") +
-  theme(legend.position = "none") -> temp
+  labs(x = NULL, y = "Mean air temperature (C)") +
+  theme(legend.position = "none",
+        strip.text = element_markdown(face = "bold", size = 11),
+        plot.background = element_rect(fill = "#F9F6EE"),
+        panel.background = element_rect(fill = "#F9F6EE")) -> fig1
+
 ggsave("weather.png", height = 3, width = 6)
 ```
+
+```{r}
+weather2 %>% 
+  filter(month %in% c(5, 6, 7, 8, 9, 10)) %>% 
+  group_by(month_lab, site, year) %>% 
+  summarise(pp = sum(pp)) %>% 
+  mutate(pp_in = pp / 2.54) |> 
+  mutate(year = as.character(year),
+         highlight = ifelse(year %in% c("2018", "2019"), TRUE, FALSE),
+         variable = if_else(highlight == TRUE, year, "NA")) -> weather2_pp
+```
+
+```{r}
+weather2_pp |> 
+  filter(variable == "NA") |> 
+  ggplot(aes(x = month_lab, y = pp_in, fill  = variable)) +
+  geom_bar(data = weather2_pp |> filter(variable != "NA"),
+           position = position_dodge2(width = 0.4),
+           stat = "identity") +
+  geom_jitter(alpha = 0.05, position = position_jitter(seed = 242)) +
+  scale_fill_manual(values = c(2, 4, "#333333")) +
+  theme_bw() +
+  labs(x = NULL, y = "Precipitation (in)") +
+  geom_richtext(data = text1, aes(x = 3.2, y = 126), lineheight = 0.4, 
+            label = "Monthly sum precipitation <br>in <b style='color:red;'>2018</b> and <b style='color:blue;'>2019</b>", size = 2, 
+            label.color = NA, fill = NA, inherit.aes = FALSE) +
+  geom_richtext(data = text2, aes(x = 3, y = 126), lineheight = 0.4, 
+            label = "30 years <br>monthly sum <br>precipitation", size = 2, 
+            label.color = NA, 
+            fill = NA, 
+            alpha = 0.5, 
+            color = "#333333",
+            inherit.aes = FALSE) +
+  geom_curve(data = text2, 
+             x = 3.6, y = 125, 
+             xend = 3.95, yend = 126,
+             alpha = 0.5, 
+             arrow = arrow(length = unit(0.05, "inch")), 
+             size = 0.4, curvature = -0.3, color = "#333333",
+             inherit.aes = FALSE) + 
+  facet_grid(~ site) +
+  theme(legend.position = "none",
+        strip.text = element_markdown(face = "bold", size = 11),
+        plot.background = element_rect(fill = "#F9F6EE"),
+        panel.background = element_rect(fill = "#F9F6EE")) -> fig2
+
+ggsave("pp_in.png", height = 3, width = 6)
+```
+
+```{r}
+library(patchwork)
+```
+
+```{r}
+fig1 / fig2 +
+  plot_annotation(tag_levels = 'A')
+
+ggsave("pp_ine.png", height = 6, width = 6)
+```

### 2021-10-21 paper.Rmd
as

@@
         legend.position = "none",
-        plot.background = element_rect(fill = "#F5F5F5"),
-        panel.background = element_rect(fill = "#F5F5F5"),
+        plot.background = element_rect(fill = "#F9F6EE"),
+        panel.background = element_rect(fill = "#F9F6EE"),
         axis.text = element_markdown(color = "#333333")) -> fig1
 
-ggsave("figures/Figure 2.png", width = 5, height = 4)
+#ggsave("figures/Figure 2.png", width = 5, height = 4)
 ```
@@
         legend.position = "none",
-        plot.background = element_rect(fill = "#F5F5F5"),
-        panel.background = element_rect(fill = "#F5F5F5"),
+        plot.background = element_rect(fill = "#F9F6EE"),
+        panel.background = element_rect(fill = "#F9F6EE"),
         axis.text = element_markdown(color = "#333333")) -> fig2
-
-ggsave("figures/Figure 22.png", width = 5, height = 4)
+#ggsave("figures/Figure 22.png", width = 5, height = 4)
 ```
@@
 ```{r}
-fig1 / fig2 / fig3 +
+fig1 / fig2 +
   plot_annotation(tag_levels = 'A')
 
-ggsave("figures/Figure 2.png", width = 6, height = 12)
+ggsave("figures/Figure 3.png", width = 6, height = 8)
 ```
@@
   bind_rows(epred2_2) %>% 
-  bind_rows(epred5) |> 
+#  bind_rows(epred5) |> 
   mutate(herbicide = fct_recode(herbicide,
@@
         legend.position = "none",
-        plot.background = element_rect(fill = "#F5F5F5"),
-        panel.background = element_rect(fill = "#F5F5F5"),
+        plot.background = element_rect(fill = "#F9F6EE"),
+        panel.background = element_rect(fill = "#F9F6EE"),
         axis.text = element_markdown(color = "#333333")) -> fig2
 
-ggsave("figures/Figure 4.png", width = 6, height = 4)
+ggsave("figures/Figure 5.png", width = 6, height = 4)
 ```

### 2021-10-25 paper.Rmd
zx

@@
 library(tidytext)
-```
-
-```{r}
 library(rstanarm)
@@
 ```{r echo=TRUE, message=FALSE, warning=FALSE}
-data <- read_csv("SB12.csv")
+data <- read_csv("data/SB12.csv")
 ```
@@
   facet_grid(year ~ location)
+```
+
+```{r}
+new_dt |> 
+  group_by(herbicide) |> 
+  summarise(control = mean(wt_28))
 ```
